Finally Tagless, Partially Evaluated

### 2008-11-06 tagless/tagless-final.tex
Mention PCF

Figure~\ref{fig:object} shows our object language, a simply-typed
$\lambda$-calculus with fixpoint, integers, booleans, and comparison.
The language is close to \citets{xi-guarded}, without their polymorphic
lift but with more constants so as to more conveniently express Fibonacci,
factorial, and power.
In contrast to \S\ref{intro}, in the rest of the paper 
we use higher-order
abstract syntax (HOAS) \citep{miller-manipulating,pfenning-higher-order}
rather than de Bruijn indices to encode binding and
ensure that our object programs are closed.
We find HOAS to be more convenient, but we have also implemented our
approach using de Bruijn indices
(in \S\ref{S:de-Bruijn} and the accompanying source file
|incope-dB.ml|).

>>>>

Figure~\ref{fig:object} shows our object language, a simply-typed
$\lambda$-calculus with fixpoint, integers, booleans, and comparison.
The language is similar to \citearound{'s PCF}\citet{plotkin-lcf}.
It is also close to \citets{xi-guarded}, without their polymorphic
lift but with more constants so as to more conveniently express examples.
In contrast to \S\ref{intro}, in the rest of the paper 
we use higher-order
abstract syntax (HOAS) \citep{miller-manipulating,pfenning-higher-order}
rather than de Bruijn indices to encode binding and
ensure that our object programs are closed.
We find HOAS to be more convenient, but we have also implemented our
approach using de Bruijn indices
(in \S\ref{S:de-Bruijn} and the accompanying source file
|incope-dB.ml|).
